\documentclass{flypcv}

\defaultmetaformat{\rmfamily\small}

\setlength{\titleheight}{0.3in}
\setlength{\headvspace}{4pt}

\author{Noah D. Ortiz}
\title{mathematics major and mentor}
\location{Caltech, MSC 772, Pasadena, CA 91126}
\email{analyticalnoa@gmail.com}
\phone{505/235-1413}

\begin{document}

  \maketitle

  \section{traits}
    \blurbcvitem{Educational}{%%
      Avidly seeks opportunities to share understanding, motivate conceptual
      thinking, and ignite discovery.%%
    }

    \blurbcvitem{Analytical}{%%
      Passionately tears systems, concepts, and problems apart to discover
      internal consistencies, discrepancies, and potential.%%
    }

    \blurbcvitem{Organizational}{%%
      Delights in version control, cataloging, writing documentation, planning,
      and improving a system's consistency/simplicity.%%
    }

    \collectcvitem{Proficient at}{%%
      Git, Linux/Unix, Mathematica, Python, \LaTeX, GnuCash, Excel%%
    }{}

  \section{education}
    \headcvitem{Manzano High School{\normalfont, Albuquerque, NM}}
      {GPA 4.75, Rank 5/327}{Class of 2018}
    \detailcvitem{Awarded ``Mathematics Student of the Year''}{}{May 2018}

    \headcvitem{Dual-Credit Program / University of New Mexico}{GPA 4.08}
      {2016--2018}
    \detailcvitem{Complex Analysis, Physics, Intermediate German}{}{}

    \headcvitem{California Institute of Technology}
      {current freshman}{Class of 2022}
    \detailcvitem{%%
      Peer Advocate, Course Ombudsperson, Board of Control Representative
    }{}{2019--present}

  \section{employment}
    \headcvitem{``STAR Fellowship''}
      {Materials Characterization, Sandia National Laboratories}{Summer 2017}
    \detailcvitem{Materials data analysis and Keyence microscope imaging.}{}{}
    \detailcvitem{Support staff for ASM Teachers Materials Science Camp.}{}{}
    \detailcvitem{Developed IGOR Pro procedure for parsing data.}{}{}

    \headcvitem{Private Tutoring}{mathematics and physics}{}
    \detailcvitem{A community college student}
      {Algebra, Calculus I}{Summer 2016--Spring 2017}
    \detailcvitem{An online college student}
      {Calculus I and II, Physics I}{Fall 2016--Spring 2018}
    \detailcvitem{A high-school junior}{Algebra II}{Spring 2018}
    \detailcvitem{An online high-school freshman}{Algebra I}{Summer 2018}

    \headcvitem{Camp Instructor / Teaching Assistant}
      {Pasadena Educational Foundation}{Summer 2019--present}
    \detailcvitem{%%
      Taught problem solving skills and guided students to develop attainable
      yet challenging research questions.
    }{}{}

  \section{volunteer}
    \headcvitem{Horizons Tutoring at Explora Museum}
      {elementary mathematics and reading}{Spring 2017--Spring 2018}
    \detailcvitem{%%
      Tutored third to sixth graders in the Horizons Albuquerque enrichment
      program.%%
    }{}{}

    \headcvitem{Tutor at Manzano High}
      {independently and via extracurricular organizations}{2014--2018}
    \detailcvitem{%%
      Assisted mathematics teachers tutor peers in algebra through calculus.%%
    }{}{}
    \detailcvitem{%%
      Tutored physics, writing, and mathematics via NHS, MESA, and Math Club.%%
    }{}{}

    \headcvitem{Rise Tutoring Program, Caltech Y}
      {mathematics, science}{Fall 2018--present}
    \detailcvitem{%%
      Tutoring students of the Pasadena Unified School District in STEM
      subjects.%%
    }{}{}

  \section{references}
    \blurb{Available upon request.}

\end{document}
